Enter our title here

### 2017-08-31 manuscript.tex

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education. By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).

The goal for any introductory statistics course is to help students develope the ability to think statistically
\citep{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
learning management systems (LMS).

@@

TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without
any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and
all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.

>>>>

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education. By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \cite{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
classroom \cite{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).

The goal for any introductory statistics course is to help students develope the ability to think statistically
\cite{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \cite{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
learning management systems (LMS).

@@

TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\cite{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without
any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and
all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.
